Pillar 1 - Sequential Pattern Mining

### 2019-02-14 Pillar 1 - Sequential Pattern Mining.Rmd
function to compute confidence and lift

  # lhs: past, rhs: present
  select(
    sequenceID,
    lhs = course_so_far,
    rhs = course_current
  )
```

@@

@@

  # Confidence and Lift by hand
  group_by(
    lhs,
    rhs_course
    ) %>%
  mutate(
    lhs.rhsTake.support = sum(support), # Proba of lhs and taking rhs course
    lhs.rhsTake.count   = lhs.rhsTake.support * n_students
    ) %>%
  ungroup %>%

@@

  # Confidence and Lift
  mutate(
    rhs.taken = str_detect(rhs, "fail|pass")
    ) %>%
  group_by(
    lhs,
    rhs_course
    ) %>%
    mutate(
    lhs.rhsTake.support = sum(support * rhs.taken), # Proba of lhs and taking rhs course
    lhs.rhsTake.count   = lhs.rhsTake.support * n_students
    ) %>%
  ungroup %>%

  # lhs and rhs must be fail, count >= 5
  filter(
    str_detect(lhs, "not taken"),
    str_detect(rhs, "fail")
    )
```

@@

  # Confidence and lift
  group_by(
    lhs, 
    rhs_course
    ) %>%
  mutate(
    lhs.rhsTake.support = max(support),
    lhs.rhsTake.count   = lhs.rhsTake.support * n_students,
    confidence          = support / lhs.rhsTake.support,
    lift                = confidence / rhs.support
    ) %>%
  ungroup %>%

@@

  # Confidenca and lift by hand
  group_by(
    lhs,
    rhs_course
    ) %>%
  mutate(
    lhs.rhsTake.support = sum(support), # Proba of (lhs => taking rhs course)
    lhs.rhsTake.count   = lhs.rhsTake.support * n_students
  ) %>%
  ungroup %>%

@@

#### not take -> fail
```{r SR TPF, eval = FALSE}
#
# SR

x <- d_transcript_cum %>%

  # rhs
  unnest(
    rhs,
    .drop = FALSE
    ) %>%
  filter(
    str_detect(rhs, "low")
    ) %>%

@@

  # support
  count(
    lhs,
    rhs
    )
```

@@

  # Confidence & lift
  group_by(
    lhs,
    rhs_course
    ) %>%
  mutate(
    lhs.rhsTake.support = max(support),
    confidence          = support / lhs.rhsTake.support,
    lift                = confidence / rhs.support
    ) %>%
  ungroup %>%

@@

## Editing rules
The function edit_rules makes AR easier to read. It keeps only rules that appear more than 5 times, rounds numerical variables to 5 significant digits, and drops aiding columns which were only used for computation in previous stages but add no additional information.
```{r edit_rules}
edit_rules <- function(AR){

@@

```{r show rules}
print(AR$TPF)
print(SR$HL)
```

>>>>

  # lhs: past, rhs: present
  select(
    lhs = course_so_far,
    rhs = course_current
  )
```

@@

### compute_conf_lift

```{r}
compute_conf_lift <- function(rules){

  # support (and count) of doing lhs and taking course of rhs
  group_by(
    lhs,
    rhs_course
    ) %>%
    mutate(
      lhs.rhsTake.support = sum(support),
      lhs.rhsTake.count   = lhs.rhsTake.support * n_students
      ) %>%
    ungroup %>%

    mutate(
      confidence = support / lhs.rhsTake.support,
      lift       = confidence / rhs.support
      )

@@

  compute_conf_lift %>%

@@

  # Confidence and Lift
  filter(
    str_detect(rhs, "fail|pass") # only keep rhsTake for computing confidence and lift
    ) %>%
  compute_conf_lift %>%

  # lhs and rhs must be fail, count >= 5
  filter(
    str_detect(lhs, "not"),
    str_detect(rhs, "fail")
    )
```

@@

  # Confidence and lift
  group_by(
    lhs, 
    rhs_course
    ) %>%
  mutate(
    lhs.rhsTake.support = max(support),
    lhs.rhsTake.count   = lhs.rhsTake.support * n_students
    ) %>%
  ungroup %>%

@@

  compute_conf_lift %>%

@@

### not take -> fail
```{r SR TPF, cache = TRUE}
SR$TPF <- d_transcript_cum %>%

  # rhs
  unnest(
    rhs,
    .drop = FALSE
    ) %>%
  filter(
    str_detect(rhs, "pass|fail")
    ) %>%

@@

  # rule
  unite(
    col = "rule",
    lhs, rhs,
    sep = " => "
    ) %>%

  # rule support
  count(
    rule
    ) %>%
  mutate(
    support = n / n_students
    ) %>%

  # regular fucntions
  clean_rules %>%

  compute_rhs.support(
    data_support = d_support$PF_HL,
    type_rule    = rate.fail
    ) %>%

  compute_conf_lift %>%

  # lhs not, rhs low
  filter(
    str_detect(rhs, "fail")
    )
```

@@

  # Confidence & lift
  group_by(
    lhs,
    rhs_course
    ) %>%
  mutate(
    lhs.rhsTake.support = max(support),
    lhs.rhsTake.count   = lhs.rhsTake.support * n_students
    ) %>%
  ungroup %>%

@@

## Editing rules
The function edit_rules makes AR easier to read. It keeps only rules that appear more than 5 times, rounds numerical variables to 5 significant digits, and drops aiding columns which were only used for computation in previous stages but add no additional information.
```{r edit_rules}
edit_rules <- function(rules){

@@

```{r show rules}
print(AR$TPF)
print(SR$TPF)
```
